### 2014-04-25 article.tex
Add in timestep to P2.
Add observations stations to fowey map.
Add P1 bathymetry image, and hotspot image.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=9cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
    \caption{Location map of the Fowey Estuary study area, southwest England, UK. }
    \label{fig:fowey_estuary_map}
\end{figure}

@@

\subsubsection{Bathymetry}
A representative sample of the bathymetry used was is shown in Figure TODO. The bathymetry was interpolated onto the mesh using the nearest four nodes for each data point, the result of which can also be seen in Figure TODO.

@@

\subsection{Dredging scenario}

@@

@@

MIKE SHE is typically calibrated by modifying the parameters listed in Table \ref{table:calibration_parameters} \parencite{refsgaard1997parameterisation, thompson2004simulation}. Following \textcite{klemevs1986operational}, the split-sample method was used. The calibration period was from 01/01/1971 to 31/12/1975, and the validation period was from 01/01/1976 to 31/12/1980. One year, 1970, was used for model spin-up time. The model was run with a timestep of (TODO: Not sure find out!).

>>>>

\begin{figure}[hbp]
    \centering
    \includegraphics[width=9cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
    \caption{Location map of the Fowey Estuary study area, southwest England, UK. The four observation points are marked with red circles. They are (North to South): Upstream, Mid-Estuary, Berth and Inlet. }
    \label{fig:fowey_estuary_map}
\end{figure}

@@

\subsubsection{Bathymetry}
A representative sample of the bathymetry used was is shown in Figure \ref{fig:raw_to_interp_bathymetry}. The bathymetry was interpolated onto the mesh using the nearest four nodes for each data point, the result of which can also be seen in Figure \ref{fig:raw_to_interp_bathymetry}.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical1/raw_to_interp_bathymetry}
    \caption{Observed bathymetry (top) and the corresponding bathymetry after it has been interpolated onto the model mesh (bottom). Scale is in \SI{}{m}.}
    \label{fig:raw_to_interp_bathymetry}
\end{figure}

@@

\newpage
\subsection{Dredging scenario}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/delta_vel_mag_depth}
    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
    \label{fig:delta_vel_mag_depth}
\end{figure}

@@

MIKE SHE is typically calibrated by modifying the parameters listed in Table \ref{table:calibration_parameters} \parencite{refsgaard1997parameterisation, thompson2004simulation}. Following \textcite{klemevs1986operational}, the split-sample method was used. The calibration period was from 01/01/1971 to 31/12/1975, and the validation period was from 01/01/1976 to 31/12/1980. One year, 1970, was used for model spin-up time. The model was run with a timestep of \SI{24}{hours}.
